Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-12 paper/ijcai16.tex
paper: fix typeface.
paper: refine the experiments section.

Equations \ref{eq:wbounds} and \ref{eq:xbounds} ensure that the obtained weight
vectors and generated configurations are in fact feasible, while the remaining
two guarantee the non-negativity of the slack and margin variables.  The
non-negativity of the $\vw^{i}$'s can be subsumed by Eq~\ref{eq:wbounds}
by choosing $w^\bot \ge 0$.

@@

\paragraph{Synthetic Dataset.} As a first test, we evaluated the performance
of the three methods on a synthetic dataset, where all configurations

We ran all methods on $20$ different users. The hidden, true weight vectors
were the same for all three methods.

>>>>

Equations \ref{eq:wbounds} and \ref{eq:xbounds} ensure that the obtained weight
vectors and generated configurations are in fact feasible, while the remaining
two guarantee the non-negativity of the slack and margin variables.  The
non-negativity of the $\vw^{i}$'s can be subsumed by Eq~\ref{eq:wbounds}
by choosing $\vw^\bot \ge 0$.

@@

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first experiment
we evaluate the behavior of the proposed method in a challenging artificial
setting. We developed seven synthetic datasets: each dataset involves
$n=2,\ldots,7$ attributes, where each attribute takes one of $n$ possible
values. More explicitly, for $n=2$ the synthetic dataset is
$\calX_\text{feasible} = [2] \times [2]$, for $n=3$ to $\calX_\text{feasible} =
[3] \times [3] \times [3]$, and so on. The cardinality of
$\calX_\text{feasible}$ is $n^n$, and grows (super-)exponentially with $n$. For
$n=3$, the dataset is comparable to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal} (which have three domains
of size of 2, 2 and 5, respectively, for a total of 20 feasible
configurations), while for larger $n$ it grows much larger than those typically
used in the Bayesian preference elicitation literature, and as such represents
a good test bed for comparing the scalability of the various methods.

The integer attributes were binarized using a standard one-hot encoding. The
feasible configuration space was encoded in {\sc SetMargin} through appropriate
MILP constraints (namely, mutual exclusivity of all binary variables
corresponding to each attribute, to enforce the one-hot encoding), while the
other methods required all datasets to be explicitly grounded.

The user weight vectors were sampled from four different distributions to
simulated different kinds of users. The first two were chosen as
in~\cite{guo2010real}: a uniform distribution over $[0, 100]$ and a normal
distribution with mean $25$ and variance $\frac{25}{3}$. In order to assess our
method in a truly sparse setting, we obtained a set of sparse normal and
uniform weight vectors by randomly deleting $80\%$ of the non-zero entries from
the already sampled vectors. We will refer to the four settings as {\sc
normal}, {\sc uniform}, {\sc sparse\_normal} and {\sc sparse\_uniform}. We
sampled a total of $100$ weight vectors for each setting. All methods were
evaluated on the very same weight vectors.
